# Recent Recipients and Projects of Switzerland's Support for Data

This section provides an overview of Statistical’s statistical activities including top country recipients and information of all projects in 2017-2020. 

## Recipients of Switzerland's Support for Data and Statistics

In 2017-2020, Switzerland provided USD 37 million of support for data and statistics.

``` {r recipients, echo = FALSE, message = F}
source("code/00. boot.R")
df_switzerland_recipients <- readRDS("~/dropbox/PARIS21/R/PRESS/Data/Intermediate/80.3 Switzerland recipients.RDS")

df_switzerland_recipients %>% 
  mutate(disbursement = round(disbursement/1000000, 3)) %>% 
  select(`Recipient Name` = recipientname, 
         `Recipient ode` = recipientcode, 
         `Disbursements (USD million)` = disbursement# , 
         # `Project name` = projecttitle, 
         # `Sector` = sectorname, 
         # `CRS ID` = crsid
         # `IDA recipient` = ida, 
         # `Fragile states` = fs 
  )%>% 
  kbl(escape = F
      , caption = "Recipients of Switzerland (2017-2020)") %>% 
  kable_paper("hover"
              , full_width = F
              # , font = "Cambria"
  )

```

## Projects of Switzerland's Support for Data and Statistics

In 2017-2020, Switzerland funded 64 projects for data and statistical development. 

``` {r other-donors, echo = FALSE, message = F}

df_switzerland_projects <- readRDS("~/dropbox/PARIS21/R/PRESS/Data/Intermediate/80.3 Switzerland projects.RDS")

df_switzerland_projects %>% 
  mutate(disbursement = round(disbursement, 3)) %>% 
  select(Recipient = recipientname, 
         `Disbursements (USD million)` = disbursement, 
         `Project name` = projecttitle, 
         `Sector` = sectorname, 
         `CRS ID` = crsid
         # `IDA recipient` = ida, 
         # `Fragile states` = fs 
         )%>% 
  kbl(escape = F
      , caption = "List of projects") %>% 
  kable_paper("hover"
              , full_width = F
              # , font = "Cambria"
  )



```
