# Recent Recipients and Projects of Switzerland's Support for Data

This section provides an overview of Switzerland’s statistical activities, including top country recipients, other active donors to coordinate with and potential aid orphans in 2017-2020. 

## Projects of Switzerland's Support for Data and Statistics

In 2017-2020, Switzerland funded 64 projects for data and statistical development. 

``` {r other-donors, echo = FALSE, message = F}

df_switzerland_projects <- readRDS("~/dropbox/PARIS21/R/PRESS/Data/Intermediate/80.3 Switzerland projects.RDS")

df_switzerland_projects %>% 
  mutate(disbursement = round(disbursement, 3), 
         projecttitle = stringr::str_replace(projecttitle, "([[:alpha:]])", toupper)) %>% 
  select(`Project name` = projecttitle, 
         Recipient = recipientname, 
         `Disbursements (USD million)` = disbursement, 
         `Sector` = sectorname, 
         `CRS ID` = crsid
         # `IDA recipient` = ida, 
         # `Fragile states` = fs 
         )%>% 
  kbl(escape = F
      , caption = "List of projects by Switzerland in 2017-2020") %>% 
  kable_paper("hover"
              , full_width = F
              # , font = "Cambria"
  )%>% 
  kable_styling(fixed_thead = T) %>%
  scroll_box(width = "100%", box_css = "border: 0px;"
             , height = "600px") 



```


## Recipients of Switzerland's Support for Data and Statistics

In 2017-2020, Switzerland provided USD 37 million of support for data and statistics.

``` {r recipients, echo = FALSE, message = F}
source("code/00. boot.R")
df_switzerland_recipients <- readRDS("~/dropbox/PARIS21/R/PRESS/Data/Intermediate/80.3 Switzerland recipients.RDS")

df_switzerland_recipients %>% 
  mutate(disbursement = round(disbursement/1000000, 3)) %>% 
  select(`Recipient Name` = recipientname, 
         `Recipient ode` = recipientcode, 
         `Disbursements (USD million)` = disbursement# , 
         # `Project name` = projecttitle, 
         # `Sector` = sectorname, 
         # `CRS ID` = crsid
         # `IDA recipient` = ida, 
         # `Fragile states` = fs 
  )%>% 
  kbl(escape = F
      , caption = "Recipients of Switzerland's support for data and statistics in 2017-2020") %>% 
  kable_paper("hover"
              , full_width = F
              # , font = "Cambria"
  ) %>% 
  kable_styling(fixed_thead = T) 
```

